\textcolor{sage}{Does Hospital Leadership Matter? \newline Evidence from Pay-for-Performance}

### 2024-11-13 Slides/JobTalk.tex

\usepackage{tikz}
\usepackage{verbatim}
\setbeamertemplate{note page}{\pagecolor{yellow!5}\insertnote}
\usetikzlibrary{positioning}
\usetikzlibrary{snakes}
\usetikzlibrary{calc}
\usetikzlibrary{arrows}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{shapes.misc}
\usetikzlibrary{matrix,shapes,arrows,fit,tikzmark}
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{multimedia}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bbm}
\newcolumntype{d}[0]{D{.}{.}{5}}
\usepackage{subfigure}
\usepackage{import}

@@

\setbeamertemplate{blocks}[rounded]
\setbeamercolor{block title}{bg=eggplant!70, fg=white}
\setbeamercolor{block body}{bg=eggplant!20}

@@

\setbeamercolor{frametitle}{fg=black, bg=lightcyan}
\setbeamercolor{title}{fg=black}
\setbeamertemplate{footline}{%
  \raisebox{5pt}{\makebox[\paperwidth]{\hfill\makebox[15pt]{\scriptsize\insertframenumber}}}}
\setbeamertemplate{navigation symbols}{} 
\setbeamertemplate{itemize items}{$\bullet$}
\setbeamercolor{itemize item}{fg=lightcyan}
\setbeamercolor{itemize subitem}{fg=lightcyan}
\setbeamercolor{enumerate item}{fg=black}
\setbeamercolor{enumerate subitem}{fg=black}
\setbeamercolor{button}{bg=eggplant!20,fg=black}

@@

% Title Slide
\begin{frame}[plain]
% Background image
\begin{tikzpicture}[remember picture,overlay]
    \node
[
    above=0.5cm,
    align=center,
    fill=lightcyan,
    rounded corners,
    inner xsep=15pt,
    inner ysep=10pt, 
    minimum width=0.9\textwidth,
    text width=0.6\textwidth
] (title) at (current page.center)
{
    \LARGE Does Hospital Leadership Matter?  \\[5pt]
    \normalsize Evidence from Pay-for-Performance
};
% Author 
\node[below=1cm] (author) at (title.south){Hanna Glenn, Emory University};
% Date
\node[below=0.25cm] (date) at (author.south){\today};
\end{tikzpicture}

@@

\begin{frame}{Firm Leadership}
\centering
    \begin{tikzpicture}
        % First image (top-left)
        \node[anchor=north west] (img1) at (0, 3) {\includegraphics[width=0.55\textwidth]{Graphics/theroleleadershiphasincompanyculture.png}};
        \draw[line width=.45mm, lightcyan] (img1.north west) rectangle (img1.south east);

        % Second image (slightly down and right of the first image)
        \node[anchor=north west] (img2) at (0.28, 0.58) {\includegraphics[width=0.5\textwidth]{Graphics/linkingbusinessstrategyandleadershipforbetteroutcomes.png}};
        \draw[line width=.45mm, lightcyan] (img2.north west) rectangle (img2.south east);

        % Fourth image (bottom-right)
        \node[anchor=north west] (img4) at (0, -2) {\includegraphics[width=0.55\textwidth]{Graphics/theroleofleadershipinorganizationalsuccess.png}};
        \draw[line width=.45mm, lightcyan] (img4.north west) rectangle (img4.south east);

@@

\begin{frame}{Leadership Characteristics}

@@

\textbf{Gender}
\begin{itemize}
    \item \small More female board members $\implies$ lower firm value \scriptsize(\cite{ahern2012changing}) \small
    \item \small More female board members $\implies$ less employment reduction \scriptsize (\cite{matsa2013female}) \small
    \item female executives affect the female wage distribution \scriptsize (\cite{flabbi2019female}) \small
\end{itemize}

@@

\textbf{Background}
\begin{itemize}
    \item \small Firms pay more for general background CEOs \scriptsize (\cite{custodio2013generalists}) \small
    \item \small CEOs w/ prior experience do better in M\&A \scriptsize(\cite{custodio2013ceos}) \small
    \item \small Military experience CEOs are less aggressive in R\&D and investing \scriptsize (\cite{benmelech2015military})
\end{itemize}

\textbf{Age}
\begin{itemize}
    \item \small Young male CEOs more aggressive in M\&A \scriptsize (\cite{levi2010deal})
\end{itemize}

\btVFill\pause

\begin{block}{\normalsize Gaps in Literature}
    \small 
    \begin{enumerate}
        \item Nonprofit firms: reason to believe these findings might not inform leadership in other settings
        \item Direct responses to policy changes
    \end{enumerate}
\end{block}
\end{frame}

\begin{frame}{Hospitals \& Health Care Policy Goals}

\begin{block}{This Paper}
    Examine the role of leadership in nonprofit hospitals responding to policy incentives 
\end{block}

@@

    \begin{itemize}
        \item Nonprofits drive the hospital industry \scriptsize (\cite{ASPE_2023}) \normalsize
    \end{itemize}

    \item \textbf{Policies often aim to improve the value of health care delivery}

@@

    \begin{wideitemize}
        \item It is unclear how hospital leaders view value
        \item Or whether they might play a role in achieving better value
    \end{wideitemize}

@@

\begin{frame}{Research Question}
    \centering
    \large
    Does having executives with clinical training affect response to pay-for-performance incentives of nonprofit hospitals in the US?
\end{frame}

@@

@@

\begin{wideitemize}
    \item Physicians can bring a unique combination of clinical and administration expertise that can potentially lead to better quality \scriptsize (\cite{Stajduhar_2023}, \cite{Ahmed_2022}) \normalsize

@@

    \item Not always trained in business management, which can lead to poor practices and lower quality \scriptsize (\cite{HarvardBusinessReview2018})
\end{wideitemize}

\textbf{Clinical training is potentially correlated with how the leader values quality}
\end{frame}

\begin{frame}{Preview of Findings}

\textbf{Non-clinical executive teams respond more drastically to financial incentives on quality compared to clinical executive teams}

@@

\begin{wideitemize}
    \item Non-clinical reduce readmission by 2\% more than clinical
    \item Non-clinical executive teams behave like profit-driven hospitals
\end{wideitemize}
\end{frame}

\begin{frame}{Contribution}
    \textbf{Hospital Executives/Board of Directors}
    \begin{itemize}
        \item Physician board members $\implies$ lower public donations in nonprofit hospitals \scriptsize (\cite{brickley2010board}) \normalsize
        \item No correlation between CEOs and hospital production in England \scriptsize (\cite{janke2019impact})\normalsize
        \item Public hospitals in Chile improved when older physicians were removed as CEO \scriptsize (\cite{otero2022managers}) \normalsize
    \end{itemize}

@@

    \textbf{Hospital Response to Pay-for-Performance}
    \begin{itemize}
        \item Hospitals decreased readmissions by 40\% on average, partially due to selective patient practices \scriptsize (\cite{gupta2021impacts}) \normalsize
        \item Market concentration and systems affect response \scriptsize (\cite{kunz2024assessing}) \normalsize
        \item Reward program had little impact on quality \scriptsize (\cite{us2015hospital}; \cite{norton2018moneyball}; \cite{friedson2019so})
    \end{itemize}
\end{frame}

@@

\begin{frame}{Nonprofit Hospital Executives}\label{nonprofithospexec}
\textbf{What do executives do?}

\begin{wideitemize}
    \item Board of directors selects executives
    \item Executives handle the day-to-day operations of the hospital \hyperlink{executivejob}{\beamergotobutton{executive job}} 
\end{wideitemize}

@@

\begin{wideitemize}
    \item Lots of variation in what executive teams look like
    \item Typically CEO and CFO, sometimes CMO 
    \item I focus on the team as a whole instead of specific executive roles
\end{wideitemize}

@@

\begin{frame}{Data Collection Process}
    \begin{enumerate}
        \item Get list of Employee Identification Numbers (EIN) that represent nonprofit hospitals

        \vspace{5mm}
        \item Download tax forms from 2009-2015 from Nonprofit Explorer API

        \vspace{5mm}
        \item Use Optimal Character Recognition to extract text from all of these documents

        \vspace{5mm}
        \item Write string cleaning algorithms to extract the correct name, title, position of each entry
    \end{enumerate}
\end{frame}

\begin{frame}{Merge to Other Data}
    \textbf{Hospital:} link EIN and ID number from the American Hospital Association (AHA) Survey based on name and location

    \vspace{1mm}
    \begin{itemize}
        \item \underline{AHA} data for hospital demographics
        \item \underline{Hospital Compare} data for readmission and mortality rates
        \item Center for Medicare and Medicaid Services (CMS) \underline{Case Mix Index file} for patient complexity
        \item \underline{Health Care Cost Report Information System (HCRIS)} for information on pay-for-performance rewards or penalties
    \end{itemize}

@@

    \textbf{Physician:} I use executives that self-identify as MD in the tax form data

    \begin{itemize}
        \item Manually match physician executives to \underline{NPPES} NPI number
    \end{itemize}
\end{frame}

\begin{frame}{About Pay-for-Performance Policies}
    Policies enacted in 2012 that either penalized for low quality or rewarded for high quality

    \textbf{Hospital Readmissions Reduction Program}
    \begin{itemize}
        \item If hospitals have above average readmission rates they get 1-3\% lower reimbursement rates
        \item Pneumonia, Heart Attack (AMI), Heart Failure
    \end{itemize}

    \textbf{Hospital Value-Based Purchasing Program}
    \begin{itemize}
        \item safety, efficiency, cost reductions, clinical outcomes, and community engagement, improvement combined into single score metric
        \item ``good" hospitals rewarded
    \end{itemize}

    \begin{block}{\normalsize Takeaway}
        \normalsize Most hospitals had incentive to improve quality to try to avoid meaningful penalties, which were not perfectly predictable
    \end{block}
\end{frame}

@@

\begin{frame}{Executive Teams}
    \begin{table}[ht!]
        \centering
        \begin{tabular}[t]{lccc}
        \toprule
         & Ever & Always & Never\\
         & Clinical Exec & Clinical Exec &  Clinical Exec \\
        \midrule
        Number of Executives & 4.85 & 5.25 & 3.11\\
        \addlinespace[0.2em]
        Fraction Clinical Execs & 0.20 & 0.26 & 0.0\\
        \addlinespace[0.2em]
        Has Clinical CEO & 0.25 & 0.11 & 0.0\\
        \addlinespace[0.2em]
        Has CMO & 0.53 & 0.45 & 0.15\\
        \addlinespace[0.6em]
        Number of Hospitals & 391 & 56 & 445\\
        \bottomrule
        \end{tabular}
    \end{table}
\end{frame}

\begin{frame}{Doctors on Executive Teams (N=813)}
    \begin{table}[ht!]
    \centering
    \begin{tabular}[t]{p{6cm} c}
    \toprule
     & Mean\\
    \midrule
    Age & 52.5\\
    Female & 0.11\\
    CEO & 0.16\\
    CMO & 0.31\\
    \addlinespace[0.3em]
    \multicolumn{2}{l}{\textbf{Specialty}}\\
    \hspace{1em}Internal Medicine & 0.32\\
    \hspace{1em}Family Medicine & 0.17\\
    \hspace{1em}Emergency Medicine & 0.11\\
    \hspace{1em}Surgery & 0.09\\
    \hspace{1em}Anesthesiologist & 0.04\\
    \hspace{1em}Other & 0.28\\
    \bottomrule
    \end{tabular}
    \end{table}
\end{frame}

@@

\begin{frame}{Hospital Statistics}
\vspace{-2mm}
    \begin{table}[ht!]
    \centering
    \begin{tabular}[t]{lccc}
     & Ever & Always & Never\\
      & Clinical Exec & Clinical Exec & Clinical Exec\\
    \midrule
    \addlinespace[0.3em]
    \multicolumn{4}{l}{\textbf{Hospital Characteristics}}\\
    \hspace{1em}Academic Med. Center & 0.41 & 0.52 & 0.24\\
    \hspace{1em}Number Beds & 231 & 222 & 116\\
    \hspace{1em}Physician Owned & 0.01 & 0.02 & 0.02\\
    \hspace{1em}System Affiliated & 0.58 & 0.52 & 0.44\\
    \addlinespace[0.3em]
    \multicolumn{4}{l}{\textbf{Penalty/Payment Variables}}\\
    \hspace{1em}Ever Received HVBP Incentive & 0.79 & 0.75 & 0.62\\
    \hspace{1em}Penalized for One Condition & 0.18 & 0.20 & 0.13\\
    \hspace{1em}Penalized for AMI + HF/Pneum. & 0.09 & 0.09 & 0.06\\
    \hspace{1em}Penalized for HF + Pneumonia & 0.41 & 0.39 & 0.34\\
    \hspace{1em}Penalized for All Conditions & 0.30 & 0.27 & 0.22\\
    Num. Hospitals & 391 & 56 & 445\\
    \bottomrule
    \end{tabular}
    \end{table}
\end{frame}

\begin{frame}{Raw Outcomes, controlling for baseline case mix index}
\centering
    \includegraphics[width=.9\textwidth]{Objects/outcomes_graph_presentation.pdf}
\end{frame}

\begin{frame}{Hospital Objectives}\label{hosp_obj}
\large
    \begin{equation*}
        \max_{\theta}\hspace{2mm}\alpha\pi(\theta) + (1-\alpha) u(\theta)
    \end{equation*}

    \vspace{5mm} \normalsize

    \begin{wideitemize}
        \item Profit $\pi$ and patient welfare $u$; depend on quality $\theta$
        \item Profit-driven hospitals have high $\alpha$
        \item Abstract away from quality impacting demand for care, price \hyperlink{complex_model}{\beamergotobutton{more complex model}} 
    \end{wideitemize}
\end{frame}

\begin{frame}{Choice of Quality}
Take FOC, rearrange and take derivative wrt $\alpha$:

>>>>

\usepackage{tikz}
\usepackage{verbatim}
\setbeamertemplate{note page}{\pagecolor{yellow!5}\insertnote}
\usetikzlibrary{positioning}
\usetikzlibrary{snakes}
\usetikzlibrary{calc}
\usetikzlibrary{arrows}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{shapes.misc}
\usetikzlibrary{matrix,shapes,arrows,fit,tikzmark}
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{multimedia}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bbm}
\newcolumntype{d}[0]{D{.}{.}{5}}
\usepackage{subfigure}
\usepackage{import}
\usepackage{fontawesome5}

@@

\setbeamertemplate{blocks}[rounded]
\setbeamercolor{block title}{bg=eggplant!70, fg=white}
\setbeamercolor{block body}{bg=eggplant!30}

@@

\setbeamercolor{frametitle}{fg=black, bg=lightcyan}
\setbeamercolor{title}{fg=black}
\setbeamertemplate{footline}{%
  \raisebox{5pt}{\makebox[\paperwidth]{\hfill\makebox[15pt]{\scriptsize\insertframenumber}}}}
\setbeamertemplate{navigation symbols}{} 
\setbeamertemplate{itemize items}{$\bullet$}
\setbeamercolor{itemize item}{fg=lightcyan}
\setbeamercolor{itemize subitem}{fg=lightcyan}
\setbeamercolor{enumerate item}{fg=black}
\setbeamercolor{enumerate subitem}{fg=black}
\setbeamercolor{button}{bg=eggplant!80,fg=white}

@@

% Title Slide
\begin{frame}[plain]
% Background image
\begin{tikzpicture}[remember picture,overlay]
    \node
[
    above=0.5cm,
    align=center,
    fill=lightcyan,
    rounded corners,
    inner xsep=15pt,
    inner ysep=10pt, 
    minimum width=0.9\textwidth,
    text width=0.6\textwidth
] (title) at (current page.center)
{
    \LARGE Does Hospital Leadership Matter?  \\[5pt]
    \large Evidence from Pay-for-Performance
};
% Author 
\node[below=1cm] (author) at (title.south){\large Hanna Glenn, Emory University};
% Date
\node[below=0.25cm] (date) at (author.south){\today};
\end{tikzpicture}

@@

\begin{frame}{Leadership Matters}
\centering
    \begin{tikzpicture}
        % First image (top-left)
        \node[anchor=north west] (img1) at (0, 3) {\includegraphics[width=0.75\textwidth]{Graphics/theroleleadershiphasincompanyculture.png}};
        \draw[line width=.45mm, lightcyan] (img1.north west) rectangle (img1.south east);

        % Second image (slightly down and right of the first image)
        \node[anchor=north west] (img2) at (0, -.25) {\includegraphics[width=0.75\textwidth]{Graphics/linkingbusinessstrategyandleadershipforbetteroutcomes.png}};
        \draw[line width=.45mm, lightcyan] (img2.north west) rectangle (img2.south east);

        % Fourth image (bottom-right)
        %\node[anchor=north west] (img4) at (0, -2) {\includegraphics[width=0.55\textwidth]{Graphics/theroleofleadershipinorganizationalsuccess.png}};
        %\draw[line width=.45mm, lightcyan] (img4.north west) rectangle (img4.south east);

@@

\begin{frame}{Leadership Characteristics and Firm Behavior/Performance}

\large

\textbf{Gender}
\begin{itemize}
    \item \normalsize Female board members $\implies$ lower firm value, less employment reduction \\ \scriptsize(\cite{ahern2012changing}; \cite{matsa2013female}) \normalsize
    \item Female executives $\implies$ female wage distribution \scriptsize (\cite{flabbi2019female}) \normalsize
\end{itemize}

\textbf{Prior Experience}
\begin{itemize}
    \item \normalsize General background CEOs paid more \scriptsize (\cite{custodio2013generalists}) \normalsize
    \item Background matters for acquisitions \scriptsize(\cite{custodio2013ceos}) \normalsize

@@

    \item Military experience CEOs \scriptsize (\cite{benmelech2015military})
\end{itemize}

\textbf{Age}
\begin{itemize}
    \item \normalsize Young male CEOs more aggressive in M\&A \scriptsize (\cite{levi2010deal})
\end{itemize}

\begin{frame}{Gaps in Literature}
    \large
    \begin{enumerate}
        \item Findings are limited to large, publicly traded firms

@@

        \begin{itemize}
            \item \normalsize Different objectives/incentives in other types of firms (nonprofits)
        \end{itemize}

        \item Unclear whether leadership matters when policies change incentives
    \end{enumerate}
\end{frame}

\begin{frame}{Addressing the Gaps}

    \Large
    \begin{block}{}
    \begin{center}
    I examine the role of leadership in nonprofit hospitals

    responding to policy incentives
    \end{center}
    \end{block}

\vspace{5mm} \large \pause

@@

    \begin{itemize}
        \item \normalsize Nonprofits drive the hospital industry \scriptsize (\cite{ASPE_2023}) \normalsize
    \end{itemize}

\vspace{8mm}

    \item \large \textbf{Policies often aim to improve the value of health care delivery}

@@

    \begin{wideitemize}
        \item \normalsize Unclear how leaders interact with this goal
    \end{wideitemize}

@@

\begin{frame}{Research Question}
    \centering
    \Large
    Do executives with clinical training

    affect response to pay-for-performance incentives

    of nonprofit hospitals in the US?
\end{frame}

@@

\large

@@

\begin{wideitemize}
    \item Relevant expertise \scriptsize (\cite{Stajduhar_2023}, \cite{Ahmed_2022}) \large

    \item Lack of business training \scriptsize (\cite{HarvardBusinessReview2018})
\end{wideitemize}

\vspace{12mm}

\textbf{Potentially correlated with how the leader values quality versus profit}
\end{frame}

\begin{frame}{Pay-for-Performance Incentives}
    \large
    \begin{block}{\Large Main Takeaway:}
        \large 
        \centering
        \vspace{1mm}
        Hospitals now have financial incentives to improve quality

        \vspace{1mm}
    \end{block}

    \vspace{6mm}

    \textbf{Quality: 30-day readmissions \& 30-day mortality}

    Hospital Readmissions Reduction Program
    \begin{itemize}
        \item Penalized high readmissions
        \item Pneumonia, Heart Attack (AMI), Heart Failure
    \end{itemize}

    Hospital Value-Based Purchasing Program
    \begin{itemize}
        \item Score metric determines rewards
        \item Rewards high metric
    \end{itemize}
\end{frame}

\begin{frame}{Preview of Main Findings}

\large

\textbf{Non-clinical executive teams respond more to financial incentives on quality}

\begin{wideitemize}
    \item Through readmission rates
    \item Non-clinical executive teams behave like profit-driven hospitals
\end{wideitemize}
\end{frame}

\begin{frame}{Contribution}
\large
    \textbf{Hospital Executives/Board of Directors}

@@

    \begin{wideitemize}
        \item \normalsize Physician board members $\implies$ lower public donations \scriptsize (\cite{brickley2010board}) \normalsize
        \item No correlation b/w CEOs and hospital productivity in England \scriptsize (\cite{janke2019impact})\normalsize
        \item Public hospitals in Chile improved when older physicians left CEO \scriptsize (\cite{otero2022managers}) \normalsize
    \end{wideitemize}

    \vspace{5mm}\pause

    \textbf{Hospital Response to Pay-for-Performance}

@@

    \begin{wideitemize}
        \item \normalsize Hospitals decreased readmissions \scriptsize (\cite{gupta2021impacts}) \normalsize
        \item Market concentration and systems affect response \scriptsize (\cite{kunz2024assessing}) \normalsize
        \item Rewards had little impact on quality \scriptsize (\cite{norton2018moneyball}; \cite{friedson2019so})
    \end{wideitemize}
\end{frame}

\large

@@

@@

\begin{frame}{About the Executives}\label{nonprofithospexec}

\large
\textbf{What do they do?}

\begin{wideitemize}
    \item Board of directors selects executives
    \item Executives handle the day-to-day operations of the hospital 
    \item Quality often improved from the top down \scriptsize (\cite{silow2011reducing})
\end{wideitemize}

\vspace{4mm} \pause

@@

\begin{wideitemize}
    \item Lot of variation in team organization
    \item CEO and CFO
    \item I focus on the team as a whole instead of specific executive roles
\end{wideitemize}

\hyperlink{executivejob}{\beamergotobutton{executive job}}

@@

\begin{frame}{Data Collection Process}
\begin{center}
\begin{tikzpicture}[
    node distance=3.1cm and 1.8cm,
    every node/.style={align=center, font=\normalsize},
    process/.style={rectangle, draw, rounded corners, text centered, minimum width=2.5cm, minimum height=2cm, fill=purple!30},
    output/.style={rectangle, draw, text centered, minimum width=2.7cm, minimum height=2.5cm, fill=purple},
    extract/.style={rectangle, draw, rounded corners, text centered, minimum width=2.5cm, minimum height=2cm, fill=sage!30},
    arrow/.style={thick, ->, >=stealth}
]

% Nodes
\node (step1) [process] {Hospital \\EINs};\pause
\node (step2) [process, right of=step1] {Download \\PDFs};
\draw[arrow] (step1) -- (step2); \pause
\node (step3) [process, right of=step2] {Extract\\text};
\draw[arrow] (step2) -- (step3); 
% New green box below step3
\node (extract) [extract, below of=step3, yshift=0.5cm] {Optical\\Character\\Recognition}; 
\draw[arrow] (extract) -- (step3);\pause
\node (step4) [process, right of=step3] {String\\cleaning\\algorithms};
\draw[arrow] (step3) -- (step4); \pause
\node (output) [output, right of=step4, text=white] {Executive\\Name\\Position\\Title};
\draw[arrow] (step4) -- (output);
\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}{Merge to Other Data}

\large
    \textbf{Hospital:}

    \vspace{2mm}
    \begin{wideitemize}
        \item AHA
        \item Hospital Compare
        \item CMS Case Mix Index
        \item Health Care Cost Report Information System (HCRIS)
    \end{wideitemize}

@@

    \textbf{Physician:}

    \begin{itemize}
        \item Manually match physician executives to NPPES NPI number
    \end{itemize}
\end{frame}

@@

\begin{frame}{Executive Teams}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
\toprule
 & Ever & Always & Never\\
  & Clinical Exec & Clinical Exec & Clinical Exec\\
\midrule
\addlinespace[0.3em]
Number Executives & 4.82 & 5.19 & 2.86\\
Fraction Clinical Execs & 0.20 & 0.26 & 0.00\\
Fraction Int. Medicine Execs & 0.06 & 0.08 & 0.00\\
Has a CMO & 0.55 & 0.52 & 0.07\\
Has Clinical CEO & 0.25 & 0.10 & 0.00\\
\addlinespace[0.6em]
Num. Hospitals & 452 & 62 & 385\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

\begin{frame}{Doctors on Executive Teams (N=941)}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lc}
\toprule
& Mean\\
\midrule
Age & 52.56\\
Female & 0.11\\
CEO & 0.15\\
CMO & 0.36\\
CQO & 0.09\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Specialty}}\\
\hspace{1em}Internal Medicine & 0.32\\
\hspace{1em}Family Medicine & 0.18\\
\hspace{1em}Surgery & 0.14\\
\hspace{1em}Emergency Medicine \hspace{4mm} & 0.11\\
\hspace{1em}Pediatrics & 0.06\\
\hspace{1em}Other & 0.16\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

\begin{frame}{Hospital Statistics}\label{sumstats}
\vspace{-3mm}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
 & Ever & Always & Never\\
  & Clinical Exec &Clinical Exec &Clinical Exec\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Hospital Characteristics}}\\
\hspace{1em}Academic Med. Center & 0.41 & 0.51 & 0.20\\
\hspace{1em}Number Beds & 227 & 218 & 102\\
\hspace{1em}Physician Owned & 0.01 & 0.02 & 0.02\\
\hspace{1em}System Affiliated & 0.57 & 0.56 & 0.42\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Penalty/Payment Variables}}\\
\hspace{1em}Ever Received HVBP Incentive & 0.79 & 0.77 & 0.59\\
\hspace{1em}Penalized for one condition & 0.19 & 0.25 & 0.13\\
\hspace{1em}Penalized for AMI + HF & 0.07 & 0.05 & 0.03\\
\hspace{1em}Penalized for AMI + Pneumonia & 0.02 & 0.02 & 0.02\\
\hspace{1em}Penalized for HF + Pneumonia & 0.41 & 0.40 & 0.33\\
\hspace{1em}Penalized for All Conditions & 0.31 & 0.31 & 0.20\\
\bottomrule
\end{tabular}
\end{table}
\hyperlink{forprofitstats}{\beamergotobutton{for-profit stats}}
\end{frame}

\begin{frame}{Raw Outcomes, controlling for baseline case mix index}\label{outcomes}
\begin{center}
    \includegraphics[width=.92\textwidth]{Objects/outcomes_graph_presentation.pdf}
\end{center}
    \btVFill
    \hyperlink{fp_outcomes}{\beamergotobutton{with for-profit}}
\end{frame}

\begin{frame}{Hospital Objectives: Profit versus Patient Welfare}
    \Large
    \centering
    \begin{equation*}
        \max_{\theta}\hspace{2mm} \alpha\pi(\theta) + (1-\alpha)u(\theta)
    \end{equation*}
\end{frame}

\begin{frame}[noframenumbering]{Hospital Objectives: Profit versus Patient Welfare} \Large
    \begin{equation*}
\max_{\theta}\hspace{2mm}\alpha
\tikz[baseline]{
    \node[draw=sage,rounded corners,anchor=base] (m1)
    {$\pi(\theta)$};
    \node[above of=m1, text=sage, yshift=5mm] (l1) {profit};
    \draw[-,sage] (l1) -- (m1);
}
+ (1-\alpha)\hspace{-11mm}
\tikz[baseline]{
    \node[draw=sage,rounded corners,anchor=base] (m2)
    {$u(\theta)$};
    \node[above of=m2, text=sage, yshift=5mm] (l2) {patient welfare};
    \draw[-,sage] (l2) -- (m2);
}
\end{equation*}
\end{frame}

\begin{frame}[noframenumbering]{Hospital Objectives: Profit versus Patient Welfare} \Large
    \begin{equation*}
\max_{\theta}\hspace{2mm}\alpha\pi(\hspace{-5mm}
\tikz[baseline]{
    \node[draw=purple,rounded corners,anchor=base] (m1)
    {$\theta$};
    \node[above of=m1, text=purple, yshift=5mm] (l1) {quality};
    \draw[-,purple] (l1) -- (m1);
}
\hspace{-5mm}) + (1-\alpha)u(\hspace{-5mm}
\tikz[baseline]{
    \node[draw=purple,rounded corners,anchor=base] (m2)
    {$\theta$};
    \node[above of=m2, text=purple, yshift=5mm] (l2) {quality};
    \draw[-,purple] (l2) -- (m2);
}
\hspace{-5mm})
\end{equation*}
\end{frame}

\begin{frame}[noframenumbering]{Hospital Objectives: Profit versus Patient Welfare} \Large
    \begin{equation*}
\max_{\theta}\hspace{-4mm}
\tikz[baseline]{
    \node[draw=earthyellow,rounded corners,anchor=base] (m1)
    {$\alpha$};
    \node[above of=m1, text=earthyellow, yshift=5mm] (l1) {weight on\\profit};
    \draw[-,earthyellow] (l1) -- (m1);
}
\hspace{-8mm}\pi(\theta) + \hspace{-7mm}
\tikz[baseline]{
    \node[draw=earthyellow,rounded corners,anchor=base] (m2)
    {$(1-\alpha)$};
    \node[above of=m2, text=earthyellow, yshift=5mm] (l2) {weight on\\patient welfare};
    \draw[-,earthyellow] (l2) -- (m2);
}
\hspace{-7mm}u(\theta)
\end{equation*}
\end{frame}

\begin{frame}{Choice of Quality}\label{choiceofquality}

\vspace{9mm}

\Large

    \begin{columns}
    \begin{column}{0.5\textwidth}
    \begin{center}
        \underline{Fee-for-Service}

            $\pi$ $\downarrow$ in $\theta$
    \end{center}
    \end{column}
    \begin{column}{0.5\textwidth}  %%<--- here
    \begin{center}
        \underline{Pay-for-Performance}

            $\pi$ $\uparrow$ in $\theta$
    \end{center}
    \end{column}
\end{columns}

\begin{block}{\Large Fee-for-service to Pay-for-performance}
    \centering
    \vspace{3mm}
    Higher $\alpha$ $\implies$ larger response

    \vspace{3mm}
\end{block}

\hyperlink{choiceofqualityapp}{\beamergotobutton{more details}}
\end{frame}

\begin{frame}{Informing the Empirical Analysis}

\large
    \begin{enumerate}
        \item If clinicians affect $\alpha$, they affect quality change after P4P

        \vspace{8mm}\pause
        \item If non-clinicians have higher $\alpha$, they act more like for-profits

        \vspace{8mm}\pause
        \item Mechanism could be revealing objectives or changing objectives
    \end{enumerate}
\end{frame}

\begin{frame}{Estimation}\label{est_equation}

\large
    \textbf{Compare always clinical to never clinical hospital executive teams:}

    \vspace{3mm}
    \begin{wideitemize}
        \item $y_{ht}$: weighted average readmission/ mortality rates
        \item Leverage \textit{timing} of the programs
    \end{wideitemize}

    \vspace{8mm}\pause

    Different methods:
    \begin{itemize}
        \item No weights
        \item \textbf{``Synthetic DiD" type weights} 
        \item Coarsened exact matching 
    \end{itemize}
\end{frame}

\begin{frame}{Identification Assumptions}

\large
\begin{wideitemize}
    \item Parallel trends
    \item No other 2012 event correlated with executive team and outcomes
    \item No hospital characteristics perfectly correlated with executive team
    \item No anticipation of incentive changes
    \item Stability in clinical executives not correlated with incentive change
\end{wideitemize}
\end{frame}

@@

\begin{frame}{Readmission Rates}\label{main:readrates}
\large
    \begin{columns}
    \column{0.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/read_md_nomd_synth_graph.pdf}
    \column{0.5\textwidth}
        \begin{wideitemize}
            \item Magnitude: 0.3ppt difference

            \item Large relative to effect of HRRP (1ppt)
        \end{wideitemize}

        \vspace{20mm}

        \hyperlink{int_margin}{\beamergotobutton{intensive margin}}
        \hyperlink{cmi}{\beamergotobutton{due to patient selection?}}
        \hyperlink{specifications}{\beamergotobutton{specifications}}
        \hyperlink{specialty}{\beamergotobutton{specialty}}

\begin{frame}{Mortality Rates}
\large
    \begin{columns}
    \column{0.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/mort_md_nomd_synth_graph.pdf}
    \column{0.5\textwidth}
        \begin{wideitemize}
            \item Magnitude: 0.1ppt

            \item Mortality is noisy measure 
        \end{wideitemize}
    \end{columns}
\end{frame}

\begin{frame}{Estimation}
\large
    \textbf{Compare both nonprofit leadership team types to the response of for-profits:}

    \vspace{5mm}\large
    \begin{equation*}
    y_{ht} = \beta \text{ (for-profit x post 2012)}_{ht} + \gamma_{h} + \delta_t + \epsilon_{ht}
    \end{equation*}

\begin{frame}{Hypotheses}

\large
    \textbf{Clinical leaders represent underlying objectives ($\alpha$)}

    \begin{wideitemize}
        \item Timing of the clinical leader doesn't matter 
    \end{wideitemize}

    \vspace{15mm}

    \textbf{Clinical leaders effectively change objectives ($\alpha$)}

    \begin{wideitemize}
        \item Timing of the clinical leader does matter
    \end{wideitemize}
\end{frame}

\begin{frame}{Estimation}
\large
    \begin{figure}[ht!]
\begin{center}

 \begin{tabular}{| m{15em} |}
 \hline \vspace{1mm}
 \textbf{Signaling:}\\ [0.5ex]
 \hline\hline 
 \vspace{2mm}
 Treat Group:  \hspace{15mm} Never MD \\
 \vspace{2mm}
 Comparison Group: \hspace{3mm} Ever MD  \\
 [1ex]
 \hline
 \end{tabular}
\hfil   %<---
 \begin{tabular}{|m{18em}|}
 \hline \vspace{1mm}
 \textbf{Managing:}\\ [0.5ex]
 \hline\hline
 \vspace{2mm}
 Treat Group: \hspace{11mm} MD in 2012 \\
 \vspace{2mm}
 Comparison Group:  MD not in 2012  \\
 [1ex]
 \hline
 \end{tabular}

\begin{frame}{Summary}
\large
    \textbf{We know very little about whether leaders matter in health care}

    \begin{wideitemize}
        \item This paper: non-clinical executive teams internalize financial incentives more
    \end{wideitemize}

    \textbf{Implications}
    \begin{itemize}
        \item Not all nonprofits have the same objectives
        \item More clinicians in leadership could shift objectives towards quality
    \end{itemize}

\begin{transitionframe}
\centering 
%\includegraphics[width=.2\textwidth]{Graphics/HannaGlenn_headshot.jpg}

\Large
    Thank you!

    \vspace{15mm}

    \textcolor{black}{\faEnvelope \hspace{2mm} hanna.glenn@emory.edu}

    \textcolor{black}{\faTwitter \hspace{2mm} @hannalynnglenn}
\end{transitionframe}

\begin{frame}{Choice of Quality}\label{choiceofqualityapp}
Take FOC, rearrange and take derivative wrt $\alpha$:
